### 2015-12-02 paper.tex
Discuss lack of Re-independence; resolves #26

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to the tendency of foils to stall
at higher angles of attack at higher $Re$, and the higher angle of attack ranges
seen by the blades at lower $\lambda$. These effects diminish with increasing
$Re$, which is expected as the blade boundary layers transition to turbulence
closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}. The
rotor drag coefficient curves show similar effects, but vary much less
dramatically from each other.

>>>>

Mean rotor power and drag coefficients for multiple Reynolds numbers are plotted
versus tip speed ratio in Fig.~\ref{fig:cp-curves} and Fig.~\ref{fig:cd-curves},
respectively. $C_P$ is shown to increase in general with $Re$, along with a
reduction in the optimal tip speed ratio, due to the tendency of foils to stall
at higher angles of attack at higher $Re$, and the higher angle of attack ranges
seen by the blades at lower $\lambda$. These effects diminish with increasing
$Re$, which is expected as the blade boundary layers transition to turbulence
closer to the leading edge \cite{Lissaman1983, Bachant2015-RVAT-Re-dep}.

Strict Reynolds number independence was not observed, i.e., the $C_P$ curves do
not collapse exactly onto each other. Note that the data collection was limited
at higher $Re$ and $\lambda$ due to the unsteady turbine force resonating with
the tow carriage drive belt. In contrast to the power coefficient data, the
rotor drag coefficient curves nearly collapse onto each other for $Re_D \ge 0.6
\times 10^6$.
